A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Adding an example of paste in parse

This corresponds to strings loaded from a file or to metaprogramming, \ie building new variables or functions by concatenating strings together. To detect this kind of metaprogramming, we look at the usage of the main concatenating functions in R, \c{paste}, \c{paste0} and \c{str_c}, and \PasteParsedEvals of the evals and \PasteParsedCallSite of the call sites using a parse function actually call a concatenating function.

>>>>

This corresponds to strings loaded from a file or to metaprogramming, \ie building new variables or functions by concatenating strings together, as in Listing~\ref{code:parsepaste}. To detect this kind of metaprogramming, we look at the usage of the main concatenating functions in R, \c{paste}, \c{paste0} and \c{str_c}, and \PasteParsedEvals of the evals and \PasteParsedCallSite of the call sites using a parse function actually call a concatenating function.

\begin{lstlisting}[caption={Using \c{eval} and \c{parse} to do meta-programming in package \emph{data.table}, to build the options at load time.}, label=code:parsepaste]
eval(parse(text=paste0("options(",i,"=",opts[i],")")))
\end{lstlisting}
